Exploratory Graphs Practice
===========================

Principles of Analytics Graphics
----------------------
1. Show Comparisons: 跟什麼比很重要
2. Show causality: 因果關係
3. Show multivariable data: 現實是很多變數的，盡可能在圖中表現出多個變因
	e.g 把年的資料拆成不同季節，迴歸的結果呈現不一樣
4. Integration of Evidence: 別讓tool綁架，想用花俏的方式呈現
5. Describe w/ appropriate label:
6. Content is KING

-----------------------
R Code
-----------------------

```{r}
# Loading Data
pollution <- read.csv("avgpm25.csv", colClasses = c("numeric", "character", "factor", "numeric", "numeric"))
head(pollution)
```

Try to display data

1. Five Number Summary
```{r}
summary(pollution$pm25)
```

2. Boxplot
```{r}
boxplot(pollution$pm25, col = "blue")
```

3. Histogram
```{r}
hist(pollution$pm25, col = "green")
```
```{r}
hist(pollution$pm25, col = "green", breaks = 100)
rug(pollution$pm25)
```


4. Overlaying Features
```{r}
boxplot(pollution$pm25, col = "blue")
abline(h = 12)
```

```{r}
hist(pollution$pm25, col = "green")
abline(v = 12, lwd = 2)
abline(v = median(pollution$pm25), col = "magenta", lwd = 4)
```

5. Barplot
```{r}
barplot(table(pollution$region), col = "wheat", main = "# of Counties in Each Region")
```


Simple Summary of Data
-------------------------
2-dimension
-------------------------
1. multiple/overlay 1-d plots
2. Scatterplots
3. smooth scatterplots

2-dimension to 3-Dimension
------------------------
1. Use Color, Size, Shape
2. Overlay/multiple 2-D plots, coplot
3. Spinning Plots
4. Acutal 3-D plot (but not useful)


1. Multiple Boxplot
```{r}
boxplot(pm25 ~ region, data = pollution, col = "red")
```

2. Multiple Histograms
```{r}
par(mfrow = c(2, 1), mar = c(4, 4, 2, 1))
hist(subset(pollution, region == "east")$pm25, col = "green")
hist(subset(pollution, region == "west")$pm25, col = "blue")
```


3. Scatterplots
```{r}
with(pollution, plot(latitude, pm25))
abline(h = 12, lwd = 2, lty = 2)
```

4. Scatterplots - Using Color
```{r}
with(pollution, plot(latitude, pm25, col = region))
abline(h = 12, lwd = 2, lty = 2)
```
Black dot is EAST; Red dot is WEST

5. Multiple Scatterplots
```{r}
par(mfrow = c(1, 2), mar = c(5, 4, 2, 1))
with(subset(pollution, region == "west"), plot(latitude, pm25, main = "West"))
with(subset(pollution, region == "east"), plot(latitude, pm25, main = "East"))
```

Summary
=================
* Exploratory plots are "QUICK and DIRTY"
* Let you summarize the data (usually graphically) and highly any broad features
* Explore basic questions and hypotheses (and perhaps rule them out)
* Suggest modeling strategies for the "next step"